TacticToe: Learning the Game of Tactics

### 2018-02-07 tactictoe_jv.tex
minor
comment on tuning

\item $A$ is a partial function from $\mathbb{G} \times \mathbb{T}$ to
$\mathbb{A}$. It takes a goal and a tactic and returns the node produced by the
application of the tactic to the goal. Its support $\mathit{Support}(A)$ is by 
definition $\lbrace (g,t) \in 
\mathbb{G} \times \mathbb{T}\ |\ t \in T(g)
\rbrace$.
\item If $(g,t) \in \mathit{Support}(A)$, then $t(g) = G(A(g,t))$. This is the 
main condition. The result of the application of a tactic $t$ 
to a goal $g$ is the list of goals contained in the node produced by $t$ from 
$g$.
\end{itemize}

@@

\begin{table}[ht]
\centering\ra{1.3}
\small
\begin{tabular}{llcc}
\toprule
 Technique & Parameters & Solved (1s) & Solved (60s)\\
\midrule
Tactic time out & 0.02s && 154\\
                & 0.05s (default) && 156\\
                & 0.1s && 154\\
\midrule
Orthogonalization & none & 105 & 156 \\
                  & $radius = 10$ & 121 & 156 \\
                  & $radius = 20$ (default) & 121 & 156 \\ 
                  & $radius = 40$ & 124 & 156 \\
\midrule
Abstraction       & none (default)  && 156\\ 
                  & $theorems = 8$  && 195\\
                  & $theorems = 16$ && 199\\
                  & $theorems = 32$ && 195\\
\midrule
MCTS policy & $c_{policy} = 0.4$ && 149\\
            & $c_{policy} = 0.5$ (default) && 156\\
            & $c_{policy} = 0.6$ && 153\\
\midrule
MCTS evaluation & none (best abstraction) && 199\\
				& $c_{exploration} = 1$ && 201\\ 
				& $c_{exploration} = 2$ && 203\\ 
				& $c_{exploration} = 4$ && 198\\
\midrule
ATP integration & none (best MCTS evaluation) && 203\\
                & \metis 0.1s && 216\\
                & \metis 0.2s && 212\\
                & \metis 0.4s && 212\\ 
                & \eprover && 213\\
                & \metis 0.1s + \eprover && 218\\
\bottomrule
\end{tabular}
\caption{\label{tab:tuning} Number of problem solved with different set of 
parameters for \tactictoe on a training set of 273 theorems.} 
\end{table}

>>>>

\item $A$ is a partial function from $\mathbb{G} \times \mathbb{T}$ to
$\mathbb{A}$. It takes a goal and a tactic and returns the node produced by the
application of the tactic to the goal. Its support $\mathit{Support}(A)$ is by 
definition $\lbrace (g,t) \in 
\mathbb{G} \times \mathbb{T}\ |\ t \in T(g)
\rbrace$.
\item If $(g,t) \in \mathit{Support}(A)$, then $t(g) = G(A(g,t))$. This is the 
main condition. The result of the application of a tactic $t$ 
to a goal $g$ is exactly the list of goals contained in the node produced by 
$t$ from 
$g$.
\end{itemize}

@@

\begin{table}[ht]
\centering\ra{1.3}
\small
\begin{tabular}{llcc}
\toprule
 Technique & Parameters & Solved (1s) & Solved (60s)\\
\midrule
Tactic time out & 0.02s && 154\\
                & 0.05s (default) && 156\\
                & 0.1s && 154\\
\midrule
Orthogonalization & none & 105 & 156 \\
                  & $radius = 10$ & 121 & 156 \\
                  & $radius = 20$ (default) & 121 & 156 \\ 
                  & $radius = 40$ & 124 & 156 \\
\midrule
Abstraction       & none (default)  && 156\\ 
                  & $theorems = 8$  && 195\\
                  & $theorems = 16$ && 199\\
                  & $theorems = 32$ && 195\\
\midrule
MCTS policy & $c_{policy} = 0.4$ && 149\\
            & $c_{policy} = 0.5$ (default) && 156\\
            & $c_{policy} = 0.6$ && 153\\
\midrule
MCTS evaluation & none (default + best abstraction) && 199\\
				& $c_{exploration} = 1$ && 201\\ 
				& $c_{exploration} = 2$ && 203\\ 
				& $c_{exploration} = 4$ && 198\\
\midrule
ATP integration & none (default + best abstraction && 203\\
                &  + best MCTS evaluation) &&\\
                & \metis 0.1s && 216\\
                & \metis 0.2s && 212\\
                & \metis 0.4s && 212\\ 
                & \eprover && 213\\
                & \metis 0.1s + \eprover && 218\\
\bottomrule
\end{tabular}
\caption{\label{tab:tuning} Number of problem solved with different set of 
parameters for \tactictoe on a training set of 273 theorems.} 
\end{table}

In Table~\ref{tab:tuning}, we run \tactictoe with different parameters. 
The first four techniques are tested relative to the same baseline indicated in 
the table by the tag ``default''.  This default strategy relies on a tactic 
time out of 0.05s, an orthogonalization radius of 20 and a policy coefficent of 
0.5. 
The two last techniques are tested relative 
to a baseline consisting of the best set of parameters discovered so far and 
are marked with the improvement over the ``default'' strategy.
In each subtable, each experiment differs from the current baseline by exactly 
one parameter.

Thanks to the larger search time available in this experiment, the timeout for 
each tactic can be raised from the 0.02 seconds used in \tactictoe's first 
experiment~\cite{lpar} to 0.05 
seconds. Removing tactics with similar effect as performed by the 
orthogonalization process is only beneficial when running \tactictoe for short 
period of time. It seems that the alloted time allows a strategy 
running without orthogonalization to catch up. 
It is best to predict a list of 16 theorems to instantiate arguments of type 
theorem list in tactics. At any rate, argument prediction for abstracted 
tactics is the technique that have the highest impact on the success of 
\tactictoe. Integration of ATPs being a specialization of this technique 
contributes significantly as well. Experiments involving \eprover, run the ATP
on one thread asynchronously with a timeout of 5 seconds and 128 premises. 
The fact that \metis outperforms \eprover in this setting is due to the fact 
that \metis is run with a very short timeout, allowing to close different part 
of search tree quickly. Because \metis is weaker that \tactictoe as an ATP, it 
is given less predictions. But even if a lemma essential for the proof of a 
goal is not predicted, a modification on the goal performed by a tactic can 
change its prediction to include the necessary lemma. 
This effect minimizes the drawback of relying on a small number of predictions.

The MCTS evaluation, despite relying on the largest amount of collected data, 
does not provide a significant improvement over a strategy relying on no 
evaluation. One one hand, our predictor learning abilities is 
limited. On the other hand, the evaluation function was designed to estimate 
the provability of a goal. A more accurate evaluation could be based on an 
estimation of the length of the proof required to close a goal.
